Holomorphic field theories and higher algebra

### 2022-07-10 draft.tex
added dedication title and some minor reminders

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}
%\title{Part I}

@@

\begin{document}
%\maketitle

@@

@@

\subsection{Background}

@@

\subsection{More examples of holomorphic field theories}

@@

\section{Vista: Holomorphic $\sigma$-models and higher algebras of differential operators}

>>>>

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}
\title{Holomorphic field theories and higher algebra}

@@

\begin{document}

\dedicatory{To Yuri Manin, with great admiration.}

\maketitle

\owen{mention some history (e.g., Manin!) and some recent work (CPTVV, Pridham, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}

@@

\owen{Revise to explain SYM as source for some examples above, but also add brief discussions of newer examples like twisted SUGRA and exotic super Lie algebras}

@@

\owen{More examples}

\subsection{An extended aside on perturbative quantization}

\owen{Sketch Brian's main results --- and Si's! --- and compare them with configuration space method of A-S and K for TFTs, subsequently developed by others}

@@

@@

\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and free field realization}
